\textbf{EECS 340: Assignment 1}

### 2020-01-26 assignment_1/article.tex
✨ Add sketch answer to Problem 3.
Co-Authored-By: bobbyCZT <zxc325@users.noreply.github.com>

It is a bit unintuitive about the case of $a' + b'$ for $a' \in \{A[0], A[1], ..., A[i-1]\}$ and $b' \in \{B[j+1], B[j+2], ..., B[n-1]\}$. But as the value of index $i$ ($j$) travels in an incremental (decremental) fashion in the bond of $\matthbb{Z+} \in [0, n)$; the index of $a'$ must be smaller than $i$, and the index of $b'$ must be greater than $j$. Thus, if there is any $a' + b' = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop. Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a', b')$ combination where $a' + b' = x$.

@@

\subsection{(d)}
The worst case of this algorithm is when it returns \inlinecode{False}. In such case we wil have $i$ and $j$ travel the entire bond of $\matthbb{Z+} \in [0, n)$. The loop will execute $2n$ times, thus the run time is $O(n)$.

\section{Problem 3}

>>>>

It is a bit unintuitive about the case of $a' + b'$ for $a' \in \{A[0], A[1], ..., A[i-1]\}$ and $b' \in \{B[j+1], B[j+2], ..., B[n-1]\}$. But as the value of index $i$ ($j$) travels in an incremental (decremental) fashion in the bond of $\mathbb{Z^+} \in [0, n)$; the index of $a'$ must be smaller than $i$, and the index of $b'$ must be greater than $j$. Thus, if there is any $a' + b' = x$, such loop would have been terminated immediately and we should not be able to reach to indexes $i, j$ in the \inlinecode{while} loop. Therefore, as we are now at the $i, j$ iteration of the \inlinecode{while} loop, this suggests there is no $(a', b')$ combination where $a' + b' = x$.

@@

\subsection{(d)}
The worst case of this algorithm is when it returns \inlinecode{False}. In such case we wil have $i$ and $j$ travel the entire bond of $\mathbb{Z^+} \in [0, n)$. The loop will execute $2n$ times, thus the run time is $O(n)$.

\section{Problem 3}
\subsection{Describe the process using a loop: Pseudocode}

% l = red, p = black
\begin{algorithm}
\caption{Kepler442b(m, n)}\label{Kepler442b}
\begin{algorithmic}[1]
\Procedure{}{}
\State $l \gets m$
\State $p \gets n$
\While {$(l + p) > 1$}
    \State \text{Let two individuals fight each other.}
    \If {\text{Both individuals are Lydians}}
        \State $l \gets l - 1$
    \ElsIf {\text{Both individuals are Pisidians}}
        \State $p \gets p - 2$
        \State $l \gets l + 1$
    \Else
        \State $l \gets l - 1$
    \EndIf
\EndWhile
\State \Return $l, p$
\EndProcedure
\end{algorithmic}
\end{algorithm}

\subsection{Define loop invariant and termination}
At the start of the $k^{th}$ iteration of the \inlinecode{while} loop, we must have
\begin{gather}
    l + p = m + n - (k - 1) \\
    p\bmod 2 = n \bmod 2
\end{gather}

When the \inlinecode{while} loop terminates at $l + p = 1$ there can only be two cases:
\begin{gather}
    l = 1, \ p = 0 \ \ (n \bmod 2 = 0) \\
    l = 0, \ p = 1 \ \ (n \bmod 2 = 1)
\end{gather}

Thus, we may infer that if $n$ is odd, a \textit{Pisidian} shall remain. Otherwise if $n$ is even, a \textit{Lydian} shall remain.

\subsection{Proof of loop invariant}
\subsubsection{Initialization}
At the beginning it is known that $k = 1$ and $b = n$, thus we may have:

\begin{gather}
    l + p = m + n - (k - 1) = l + p = m + n - (1 - 1) \Rightarrow l + p = m + n \\
    p\bmod 2 = n \bmod 2
\end{gather}

As the above two \textit{Equations} satisfy the assumption of the loop invariant, we may say that the scenario of $k = 1$ is true.

\subsubsection{Maintenance}

\paragraph{Case 1} As it is known that $l + p = (l - 1) + p$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.

\paragraph{Case 2} As it is known that $l + p = (l + 1) + (p - 2)$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.

\paragraph{Case 3} As it is known that $l + p = (l - 1) + p$ and $k = k + 1$, we may conclude that $l + p + k$ must remain the same.

As all three cases satisfy the loop invariant of the algorithm, the induction is therefore proven to be valid.
